Vulnerability Analysis of Container Images in Neuroimaging

### 2020-02-11 paper.tex
modification till results

%%%% Commands %%%%
\newcommand{\todo}[1]{\color{red}\textbf{TODO:}#1\color{black}}
\newcommand{\note}[2]{\color{blue}Note: #1\color{black}}
\newcommand{\reprozip}[0]{ReproZip}
\newcommand{\TG}[1]{\color{blue}From Tristan: #1\color{black}}

\title{Vulnerability Analysis of Container Images in Neuroimaging field}

@@

\author[1]{Bhupinder Kaur}
\author[1]{Tristan Glatard}
\author[1]{Aiman Hanna}

@@

@@

\subsection{Container Engines}

@@

Singularity offers mobility of compute by facilitating portable environments 
through a single image file~\cite{kurtzer2016singularity}. Once Singularity image
is created, it is hashed by using SHA256 hashing. Hence, it cannot be changed
once it is created, consequently, it can be used for reproducing the results of
scientific experiments. Main features provided by
Singularity are mobility of compute and reproducibility~\cite{kurtzer2017singularity}.
We used Singularity version $2.5.2$ in our experiments.
Users can easily access files, devices, sockets, ports of the host system from
the Singularity container. By default, Singularity bind mounts /home/\$USER, /tmp, and \$PWD
into the running container. Additional directories can be specified with \textit{--bind}
to bind mount into the container. By defaut, Singularity uses as less as possible namespaces.
However namespaces can be requested if required. Users cannot escalate privileges inside
Singularty containers. This is because Singularity do not run containers as root.
Instead, a user inside Singularity container is the same user outside the container.

\subsubsection{Docker Engine}

Docker runs a software, \textit{Docker daemon}, on the host machine.
Docker daemon runs as root, and is remotely controlled through a
UNIX socket. It is responsible for launching containers, their
isolation, and spawning shells into the containers. It is also
responsible for managing Docker images i.e \textit{pull} and \textit{push}
from image repository, building images from Dockerfiles, signing them, etc..
When a Docker container runs, the container process is spawned as a
child of this root owned daemon. As Docker users directly interact with the
Docker daemon, it is possible to force Docker daemon to escalate privileges.
If a user gets \textit{root} privileges, it introduces unthinkable security risks
for multi-tenant shared enviornments. Due to this reason, Docker is not
supported by HPC environments. However, Docker images can be imported into
Singularity and then used on HPC clusters.

@@

A container image is a package that contains the application along with its
required dependencies and libraries.
Both, Docker and Singularity, have different image format. Below we provide description of both image
formats.

@@

Docker images are organized as a series of layers stacked on top of each
other and identified by unique layer identifiers. If a layer is reused
in different images it will
have the same id across images. Each layer consists of a filesystem diff
with respect to the layer below. DockerHub uses gzip compression for
transferring layers. \begin{comment}There are two ways to create a Docker image. The
first is to use an existing Docker image as a base image and then build a
new image from that one, by making changes in the filesystem, which is
saved as a new layer of the Docker image. The second way is to build a new
Docker image from scratch.\end{comment} Docker supports several different storage drivers.
\textit{Overlay2} is the preferred storage driver used by Docker for all currently
supported Linux versions, whereas \textit{aufs} is preferred for Docker 18.06 and
older, when using Ubuntu 14.04 on kernel 3.13 as it do not support \textit{overlay2}.
Other storage drivers that are supported by Docker include \textit{devicemapper, btrfs,
zfs, and vfs}

@@

Singularity takes snapshot, locks, and archives the developed application,
which is known as Singularity image.
It means that Singularity image is a single immutable file that can be moved around as
any other file. This file can be checksummed, signed, and easily
used for verification purposes. Singularity containers use Squashfs file format
by default. It is read-only file system in Linux, which uses compression for files,
inodes, and directories. However, Singularity also supports two other 
formats i.e \textit{sandbox} format
(which is just a chroot
directory) and \textit{writable} format (the ext3 file system).
While publishing experimental results, authors can also publish Singularity
image along with its hash, which allow other researchers to verify results.

@@

@@

We used the 49 Boutiques applications published on Zenodo at the time of
the writing. These applications use 23 different container images,
including 7 Singularity images and 16 Docker images.

@@

BIDS apps~\cite{gorgolewski2017bids} is a framework designed to share and execute neuroimaging
analysis pipelines. It improves usability, accesibility, and reproducibility
of different applications through containerization.
Currently, there are 27 BIDS apps available and all are using different Docker images.
%\begin{figure}
%\csvreader[%
% respect all,%
%  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
%      %\caption{Baseline GF Competition Circle Track 2014}\label{tab:baselline1}
%      \begin{adjustbox}{max width=\columnwidth},
%  after reading=\end{adjustbox},
% tabular={c |c | c | c | c},
%	table head =Image & {OS Distro} & {Vulnerabilities by Anchore} & {Vulnerabilities by Clair} & {Vulnerabilities by Vuls}\\\hline,
% late after line= \\,
%	late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
%]{results.csv}{}{\csvlinetotablerow}%
%       \centering
%	\caption{Existing number of Vulnerabilities}
%\end{figure}

@@

BIDS app and Boutiques images that we took for our experiment have diverse Linux
distributions such as Ubuntu, Centos, Debian, and Alpine. In case of Ubuntu, release
can be of two types i.e regular or LTS(Long Term Support) release.
Regular release is supported only for 9 months, whereas LTS is supported for 5 years. Once LTS support
reaches End-Of-Life(EOL), Ubuntu decides whether to provide extended security support or not, which comes
in the form of Extended Security Maintenance(ESM) release.
ESM is a paid service that can be requested from Ubuntu to get security 
updates even after the EOL of a particular Ubuntu release. The ESM support period is decided by
Ubuntu. ESM and LTS releases of a particular Ubuntu distribution have different vulnerability
data in vulnerability databases.

Some Ubuntu distributions that are present inside images have already reached EOL such as 14.04 Long Term Support (LTS),
17.04, and 17.10. However, Ubuntu is providing ESM support for Ubuntu 14.04. The images in our experiment have Ubuntu 14.04 LTS so scanners should refer
to LTS release only while collecting data from vulnerability databases. If scanners refer to ESM release for data it may result
in false positives and false negatives.
Also, if these releases with EOL are used in images, there are no chances of getting updates, hence
resulting in vulnerable images. Additionally, even if ESM release is present for some EOL release it is
not feasible to use inside images.

@@

If there exist vulnerabilities in the container image, then we can
run after updating the
image. Updating the image involves updating all software packages that are
inside that image. We used a bash script(\href{https://github.com/kaurbhupinder/Vulnerability-Analysis}{Github}) 
to update all images, which checks
package manager present inside the image and then according to that it
updates the image. However, this option effects the reproducibility
of the image, which means that the image cannot be used to verify research
findings of other scientists.

\subsection{Scanning tools used}

Out of the various container image scanning tools available to scan Docker images,
we selected Anchore~\cite{github_2019}
and Vuls~\cite{future-architect_2019} because these are the most mature scanning tools. To scan Singularity images
we use Stools, which is specially designed for Singularity images. This tool internally uses
Clair Scanner tool so we included ClairScanner also in our experiements to compare
performance of both the tools. So total there are three scanners for Docker images
and one scanner for Singularity images.

Anchore is an end-to-end, open-source container security platform. Anchore
is a static
scanning tool that analyses container images and lists OS
packages, non-OS packages (Python, Java, Gem, and Npm), and files.
Anchore is a set of tools, which users can
employ for scanning container images and applying custom policies to them.
It provides visibility and transparency of the container environment.
It offers services in two ways: Anchore Engine and Anchore Engine
Command Line Interface (CLI). Anchore Engine is available as a Docker
image, which is available on Docker Hub. Anchore Engine CLI provides
command line interface in addition to Anchore Engine REST API. It can be
installed directly on the host and used to inspect images.
Anchore compares package versions, which are present inside the
image, with the vulnerability database to flag vulnerabilities.
To get vulnerability feed of various OS distribution, Anchore refers to
different sources. For example Ubuntu launchpad database is used for Ubuntu. 
\subsubsection{Vuls}

Vuls is an open-source vulnerability scanner for Linux and FreeBSD.
It is an agentless vulnerability scanner and uses various
vulnerability databases. Using dynamic scanning technique, it offers
remote and local scan. Remote scan involves setting up only one machine, to
which other target servers are connected via SSH. Local scan involves running
the scan on the target server itself. Further, Vuls offer fast scan, fast root scan,
and deep scan.
Fast scan is performed without root privileges, whereas fast root scan is
performed with root privileges. The latter also uses checkrestart utility to 
detect processes that are updated but not yet restarted because if they are not
restarted, updates are not effective. So fast root scan also detects these pro-
cesses. Both fast scan and fast root scan are performed offline without Internet
access, and put almost no load on the scan target server. Deep scan uses
root privileges for scanning, and is used to get a more detailed scan. It checks
changelogs, which puts more load on the target server.
Vuls gets data from Open Vulnerability and Assessment Language (OVAL).
The interesting point is that there is no OVAL data for Ubuntu 17.04 and 17.10 distribution,
meaning that images with these distributions are impossible to scan with Vuls.

CoreOS originally created Clair, which is a static vulnerability scanner for containers which
currently support App Container (appc) and Docker~\cite{coreos_2019}. The main goal of the
tool is to provide a transparent look of container’s security. Clair scans container images in regular
intervals, and stores metadata of vulnerabilities, after getting from configured
set of sources. Clair API can be used by clients to query its database to get
the list of vulnerabilities that a particular image has. Clair sends a notification
to alert systems that there is an updation in the vulnerability metadata. Quay
registery uses Clair internally as the security engine. However, Clair does not 
provide facility of comparing
the vulnerability list of a particular image against a whitelist~\cite{arminc_2019}. So to remove
that drawback, another tool from CoreOS, Clair Scanner can be used. It scans image, prepares the list of
vulnerabilities, compares that list against the whitelist, and flags vulnerabilities
that are not present in whitelist.
Clair Scanner refers to Ubuntu CVE tracker for getting Ubuntu vulnerability feed.
For that purpose a Docker image is maintained that contains Ubuntu CVE tracker database.
Whenever Ubuntu updated its database, this image is also updated with the required information.
We performed scanning on 2019-09-25 and for our experiments, we used a Docker image that was 
latest updated i.e with the tag 2019-09-18. So it means that Clair Scanner's database was
old by one week.

\href{https://github.com/singularityhub/stools}{Stools} combines CoreOS's Clair Scanner with the Continuous Integration (Travis and
Circle) for scanning Singularity images for vulnerabilities.
Initially, Clair Scanner was intented to scan Docker Containers. This tool does not fit well
to scan Singularity images because of the different image formats. Docker layers
consist of layers, whereas Singluarity images consist of a single binary file.
However, TravisCI and CircleCI are commonly used for testing code, and these
services also offer running containers. So Stools combined both the concepts.
It involves spinning a Clair Scanner container during testing and building a
Singularity image, and scanning it for filesystem before the image is finalized.

@@

In this section, we present results of three experiments that are carried out to see
how the number of vulnerabilities vary inside images. First experiment involves scanning
these images as it is to see how vulnerable they are. For scanning we use three different scanners
to see if all are reporting same vulnerabilities or not. Second experiment involves updating
all these images and then rescanning. The last experiment involves shrinking the size of the image
meaning that removing all unnecessary packages from the image to see the effect on the number of
vulnerabilities present inside the image.

@@

Figure~\ref{fig:graph1} represents the number of vulnerabilities that are present inside images.
This figure shows that as the number of packages increases in the image, the number of vulnerabilities
also get increased for Ubuntu OS distribution. The figure also infers that Alpine distribution, being the
light weight distribution, have least number of vulnerabilities, whereas Ubuntu contains highest number of
vulnerabilities. Debian contains highest number of critical vulnerabilities among Ubuntu, Alpine, and Centos.

@@

Figure~\ref{table1} shows results of scanning BIDS and Boutiques images with three scanners namely Anchore,
Clair scanner and Vuls. Venn Diagram in Figure~\cite{fig:venn} summarizes this table. It is interesting to note that
Anchore reports 4453 different vulnerabilities, which is way more than both Clair and Vuls.

The number and type of vulnerabilities reported by three scanners are drastically different from each other.
The question arises why these scanners report different number and type of vulnerabilities.
How their logic differs and what exactly is making these results different than each other.

@@

\textbf{Vulnerabilities not present in Ubuntu 14.04 ESM release-} These vulnerabilities are not present in Ubuntu 14.04 ESM so they 
are not detected by Clair but they affect Ubuntu 14.04 LTS That’s why detected by Vuls. For example, CVE-2017-1375.

\textbf{False negatives by Clair-} Clair is missing vulnerabilities that it should detect. For example CVE-2016-9082 
is present in package cairo in Xenial release and it is not detected by Clair.

\textbf{False positives by Clair-} These vulnerabilities are not linked to Ubuntu 14.04 LTS which is 
present inside the image but Clair is showing because these vulnerabilities are present in Ubuntu 14.04 ESM and 
Clair is only referring to Ubuntu 14.04 ESM release. For example CVE-2019-1274.

\textbf{Database difference-} As we discussed earlier that Clair Scanner's database was old by one week.
                So some of the vulnerabilities were not updated yet. For example CVE-2019-5094, which
		was published on 2019-09-24, was not 
		updated in Clair Scanner's database that time. Due to which it is missed by Clair Scanner.

\textbf{Epoch bug-} There is a bug in the Anchore scanner due to which some vulnerabilities are 
		not detected by Anchore. This bug gets triggered when package’s version have epoch 
		(1:3.3.9-1ubuntu2.3)  in it. For example CVE-2018-1125 in procps package.

\textbf{with status as "Ignored (out of standard support)" bug-} There is another bug in Anchore due to 
		which it is not able to detect some vulnerabilities. Due to this bug Anchore does not detect 
		vulnerabilities which have a status as “ignored (out of standard support)” in Ubuntu 14.04 LTS. 
		But if this vulnerability is present in Ubuntu 14.04 ESM release it is detected by Clair. 
		For example CVE-2019-13565 in Ubuntu 14.04.

\textbf{False Negatives by Vuls-} Vuls is missing some of the vulnerabilities that it should detect. 
		For example CVE-2019-5094

\textbf{Rejected CVEs-} There are some CVE that are rejected because they are duplicate copies of another CVEs. 
	So Anchore is not reporting those rejected CVEs but Vuls is reporting those. For example CVE-2017-13753

@@

The next experiment involves updating all these images and then rescanning them to see how the number of
vulnerabilities drop inside them. We used a \textit{bash} script to update these images. This script is
present in our github repository \href{https://github.com/kaurbhupinder/Risk-to-Clusters-Paper}
{https://github.com/kaurbhupinder/Risk-to-Clusters-Paper}. This script 
will find package manager inside the image and then update the image according the package manager it finds.
When these images are rescanned after updation, results changed drastically. However, there are still
vulnerabilities reported by these scanners but there are no fixes available for these vulnerabilities
till date so there is nothing that can be done to remove these vulnerabilties. There are only two
options, either you accept those vulnerabilities and use that image, or you discard that image.
So one thing is clear here that even if we keep our images up to date there will be still some
vulnerabilities that we have to face.
Figure~\ref{fig:graph2}shows number of vulnerabilities that are detected by Anchore after updating these images.

\begin{figure}[!htb]
        {\includegraphics[width=\columnwidth]
        {Figures/aferupdatewithpackage.png}}
        \caption{\label{fig:graph2} Scatterplot representing difference in number of vulnerabilities before and 
	after update of image}
      \end{figure}
\subsection{Effect Of Size Reduction}

>>>>

%%%% Commands %%%%
\newcommand{\todo}[1]{\color{red}\textbf{TODO:}#1\color{black}}
\newcommand{\note}[2]{\color{blue}Note: #1\color{black}}
\newcommand{\reprozip}[0]{ReproZip}
\newcommand{\rom}[1]{\lowercase\expandafter{\romannumeral #1\relax}}
\newcommand{\TG}[1]{\color{blue}From Tristan: #1\color{black}}

\title{Vulnerability Analysis of Container Images in Neuroimaging}

@@

\author[1]{Bhupinder Kaur}
\author[1]{Aiman Hanna}
\author[1]{Tristan Glatard}

@@

In this section, we present our study methodology. We first
introduce two container tools used for our experiments: Docker and
Singularity and their image formats. Then we describe Boutiques and BIDS application frameworks
from where we took containerized applications for our study. Later, we discuss about 
various Linux distributions and their releases. Lastly, this section
provides the description of the scanning tools used.

@@

\subsection{Container Tools}

Tools that are capable of packing and running an application in an isolated environment
are known as container tools. Alongwith an application they also pack the application's dependencies,
required libraries and configuration files for the
application to function properly. This functioning of an application in an isolated environment
is called a container. They directly run on the Host machine's kernel so they are lightweight.
Consequently, more containers can be run on a given Host machine as compared to virtual machines.

\subsubsection{Docker}

Docker is a tool to run containers.
Docker containers are managed by the Docker engine, which is a client-server application and
consists of the following three main components:

\textit{Docker Daemon:} It acts as a server. It is
a long running process that manages all Docker images, containers, storage volumes, and networks.

\textit{REST API:} It acts as a interface between the server and the client, and is an API which is used by the applications
to talk to the \textit{Docker Daemon}.

\textit{Client:} It is a Command Line Interface (CLI) client which is used to interact with the \textit{Docker Daemon}.

%Docker runs a software, \textit{Docker daemon}, on the host machine.
Docker daemon runs as root, and is remotely controlled through a
UNIX socket. As Docker Daemon is responsible for launching and managing containers,
when a container runs, the container is spawned as a
child process of this root owned daemon.

\begin{comment}
It is responsible for launching containers, their
isolation, and spawning shells into the containers. It is also
responsible for managing Docker images i.e \textit{pull} and \textit{push}
from image repository, building images from Dockerfiles, signing them, etc.
When a Docker container runs, the container process is spawned as a
child of this root owned daemon. 
\end{comment}
As Docker users directly interact with the
Docker daemon through CLI i.e \textit{docker} command, it is possible to force Docker daemon to escalate privileges.
If a user gets \textit{root} privileges, it introduces unthinkable security risks
for multi-tenant shared enviornments. Due to this reason, Docker is not
supported by HPC environments.

@@

Singularity is another tool for packing and running applications in containers.

Singularity offers mobility of compute by facilitating portable environments 
through a single image file~\cite{kurtzer2017singularity}. Once Singularity image
is created, it is hashed using SHA-256. Hence, it cannot be changed
once it is created, consequently, it can be used for reproducing the results of
scientific experiments. Main features provided by
Singularity are mobility of compute and reproducibility~\cite{kurtzer2017singularity}.
We used Singularity version $2.5.2$ in our experiments.
Users can easily access files, devices, sockets, ports of the host system from
the Singularity container. By default, Singularity bind mounts /home/\$USER, /tmp, and \$PWD
into the running container. Additional directories can be specified with \textit{--bind}
to bind mount into the container. By defaut, Singularity uses as less as possible namespaces.
However namespaces can be requested if required. Users cannot escalate privileges inside
Singularty containers. This is because Singularity do not run containers as root.
Instead, a user inside Singularity container is the same user outside the container.

@@

A container image is a package that contains an application along with its
required dependencies and libraries.
Both, Docker and Singularity, have different image formats. Below we provide description of both image
formats.

@@

Docker images are organized as a series of layers stacked on top of each
other and identified by unique layer identifiers. If a layer is reused
in different images it will
have the same id across images. Each layer consists of a filesystem diff
with respect to the layer below. 
\begin{comment}
DockerHub uses gzip compression for
transferring layers.There are two ways to create a Docker image. The
first is to use an existing Docker image as a base image and then build a
new image from that one, by making changes in the filesystem, which is
saved as a new layer of the Docker image. The second way is to build a new
Docker image from scratch.Docker supports several different storage drivers.
\textit{Overlay2} is the preferred storage driver used by Docker for all currently
supported Linux versions, whereas \textit{aufs} is preferred for Docker 18.06 and
older, when using Ubuntu 14.04 on kernel 3.13 as it do not support \textit{overlay2}.
Other storage drivers that are supported by Docker include \textit{devicemapper, btrfs,
zfs, and vfs}
\end{comment}

@@

On the other hand, Singularity image is a single immutable file and 
does not contain layers.
\begin{comment}
Singularity takes snapshot, locks, and archives the developed application,
which is known as Singularity image.
It means that Singularity image is a single immutable file that can be moved around as
any other file. This file can be checksummed, signed, and easily
used for verification purposes. Singularity containers use Squashfs file format
by default. It is read-only file system in Linux, which uses compression for files,
inodes, and directories. However, Singularity also supports two other 
formats i.e \textit{sandbox} format
(which is just a chroot
directory) and \textit{writable} format (the ext3 file system).
While publishing experimental results, authors can also publish Singularity
image along with its hash, which allow other researchers to verify results.

@@

BIDS apps~\cite{gorgolewski2017bids} is a framework designed to share and execute neuroimaging
analysis pipelines. It improves usability, accesibility, and reproducibility
of different applications through containerization.
At the time of this study, there were 27 BIDS apps available and all are using different Docker images.
Out of these 27 images, we used 26 images for our experiments because one of them was not available
on Docker hub.

@@

We used the 49 Boutiques applications published on Zenodo at the time of
the writing. These applications use 23 different container images. Out of these images,
3 images are not found and 2 images were already included in BIDS images.
Therefore we are left with total 18 Boutiques images which includes 6
Singularity images and 12 Docker images.

@@

BIDS apps~\cite{gorgolewski2017bids} is a framework designed to share and execute neuroimaging
analysis pipelines. It improves usability, accesibility, and reproducibility
of different applications through containerization.
At the time of this study, there were 27 BIDS apps available and all are using different Docker images.
Out of these 27 images, we used 26 images for our experiments because QAP bids app was not available
on Docker hub.

So we have total 38 Docker images from both BIDS Apps and Boutiques.
	Table~\ref{table2} displays the names of all the images that we took in our experiments.
%\begin{figure}
%\csvreader[%
% respect all,%
%  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
%      %\caption{Baseline GF Competition Circle Track 2014}\label{tab:baselline1}
%      \begin{adjustbox}{max width=\columnwidth},
%  after reading=\end{adjustbox},
% tabular={c |c | c | c | c},
%	table head =Image & {OS Distro} & {Vulnerabilities by Anchore} & {Vulnerabilities by Clair} & {Vulnerabilities by Vuls}\\\hline,
% late after line= \\,
%	late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
%]{results.csv}{}{\csvlinetotablerow}%
%       \centering
%	\caption{Existing number of Vulnerabilities}
%\end{figure}

@@

BIDS app and Boutiques images that we took for our experiment have diverse Linux
distributions such as Ubuntu, Centos, Debian, and Alpine. In case of Ubuntu, release
can be of two types : regular or LTS (Long Term Support).
Regular release is supported only for 9 months, whereas LTS is supported for 5 years. Once LTS support
reaches End-Of-Life (EOL), Ubuntu decides whether to provide extended security support or not, which comes
in the form of Extended Security Maintenance (ESM) release.
ESM is a paid service that can be requested from Ubuntu to get security 
updates even after the EOL of a particular Ubuntu release. The ESM support period is decided by
Ubuntu. ESM and LTS releases of a particular Ubuntu distribution have different vulnerability
data in vulnerability databases because after EOL of a release, a vulnerability is fixed only in packages of ESM, however, it still
exists in LTS.

Ubuntu has ended support for some releases such as 14.04 LTS,
17.04, and 17.10, which means they have reached EOL. However, Ubuntu is providing optional extended support for Ubuntu 14.04.
To use this extended support, users have to buy ESM release for Ubuntu 14.04.
The images in our experiments have Ubuntu 14.04 LTS so scanners should refer
to LTS release only while collecting data from vulnerability databases. If scanners refer to ESM release for data it may result
in false positives and false negatives.
Also, if ubuntu releases with ended support are used in images, there are no chances of getting updates, hence
resulting in vulnerable images. Additionally, even if extended security is provided for some releases by Ubuntu, it is
not feasible to use it inside images because it is a paid service.

\subsection{Scanning Images}

Scanning an image means looking into the image, collecting all the information about the image, and
finally, using this information to detect vulnerabilities present inside the image.
Scanning can be broadly categorised into two types: \rom{1} Static Scanning and \rom{2}
Dynamic Scanning.
In Static scanning, an image is scanned without running it into a container. In respect to that,
differnt image features are extracted like installed packages, their versions, files, etc.
On the other hand, Dynamic scanning involves running a container from the image and then scanning the
dynamic behaviour of the image.

\subsubsection{Scanning tools used}
\begin{comments}
Out of the various container image scanning tools available to scan Docker images,
we selected Anchore~\cite{github_2019}
and Vuls~\cite{future-architect_2019} because these are the most mature scanning tools. To scan Singularity images
we use Stools, which is specially designed for Singularity images. This tool internally uses
Clair Scanner tool so we included ClairScanner also in our experiements to compare
performance of both the tools. So total there are three scanners for Docker images
and one scanner for Singularity images.
\end{comments}

We used three scanners namely Anchore~\cite{github_2019}, Vuls~\cite{future-architect_2019}, and
Clair Scanner~\cite{arminc_2019} for scanning Docker images because these are the most
mature scanners. Out of these scanners, only Vuls uses dynamic scanning and remaining two
are static scanners.
Also, we freezed vulnerability databases for these scanners on September 25, 2019 and scanned
all images to avoid getting different results due to the differences in the scanner's database.
Lastly, for scanning Singularity images, we used Stools.

Anchore is an end-to-end, open-source container security platform. Anchore
is a static
scanning tool that analyses container images and lists OS
packages, non-OS packages (Python, Java, Gem, and Npm), and files.
\begin{comments}
Anchore is a set of tools, which users can
employ for scanning container images and applying custom policies to them.
It provides visibility and transparency of the container environment.
\end{comments}
Anchore Engine can be used in two ways: through Docker image or Anchore
Command Line Interface (CLI).
\begin{comments}
Anchore offers services in two ways: Anchore Engine and Anchore
Command Line Interface (CLI). Anchore Engine is available as a Docker
image, which is available on Docker Hub. Anchore Engine CLI provides
command line interface in addition to Anchore Engine REST API. 
\end{comments}
It can be
installed directly on the host and used to inspect images.
In our experiments, we used a Docker image to get Anchore Engine version 0.5.0 and Engine Database
version 0.0.11.

Anchore compares package versions, which are present inside the
image, with the vulnerability database to flag vulnerabilities.
To get vulnerability feed of various OS distribution, Anchore refers to
different sources. For example Ubuntu launchpad database is used for Ubuntu.

\subsubsection{Vuls}

Vuls is an open-source vulnerability scanner for Linux and FreeBSD.
Using dynamic scanning technique, it offers
remote and local scan. Remote scan involves setting up only one machine, to
which other target servers are connected via SSH. Local scan involves running
the scan on the target server itself. Further, Vuls offer fast scan, fast root scan,
and deep scan.
Fast scan is performed without root privileges, whereas fast root scan is
performed with root privileges. The latter also uses checkrestart utility to 
detect processes that are updated but not yet restarted because if they are not
restarted, updates are not effective. So fast root scan also detects these
processes. Both fast scan and fast root scan are performed offline without Internet
access, and put almost no load on the scan target server. Deep scan uses
root privileges for scanning, and is used to get a more detailed scan. It checks
changelogs, which puts more load on the target server.
Vuls gets data from Open Vulnerability and Assessment Language (OVAL).

The interesting point is that there is no OVAL data for Ubuntu 17.04 and 17.10 distribution,
meaning that images with these distributions are impossible to scan with Vuls.

CoreOS originally created Clair, a static vulnerability scanner for containers. 
\begin{Comments}
The main goal of the
tool is to provide a transparent look of container’s security. Clair scans container images in regular
intervals, and stores metadata of vulnerabilities, after getting from configured
set of sources. 
\end{comments}	
Clair API can be used by clients to query its database to get
the list of vulnerabilities that a particular image has. Clair sends a notification
to alert the systems if there is an update in the vulnerability metadata. Quay.io, which
is a registery to store images privately, uses Clair internally as the security engine. However, Clair does not 
provide facility of comparing
the vulnerability list of a particular image against a whitelist of vulnerabilities that you
want to ignore~\cite{arminc_2019}. 
So, to remove
that drawback, another tool from CoreOS, Clair Scanner can be used. It scans image, prepares the list of
vulnerabilities, compares that list against the whitelist, and flags vulnerabilities
that are not present in the whitelist.
Clair Scanner refers to Ubuntu CVE tracker for getting Ubuntu vulnerability feed.
For that purpose a Docker image is maintained that contains Ubuntu CVE tracker database.
Whenever Ubuntu updated its database, this image is also updated with the required information.

We performed scanning on 2019-09-25 and for our experiments, we used a Docker image that was 
latest updated i.e with the tag 2019-09-18. So it means that Clair Scanner's database was already
old by one week.

\href{https://github.com/singularityhub/stools}{Stools} combines CoreOS's Clair Scanner with Continuous Integration (CI)
for scanning Singularity images for vulnerabilities.
Initially, Clair Scanner was intented to scan Docker Containers. This tool does not fit well
to scan Singularity images because of the different image formats. Docker images
consist of layers, whereas Singluarity images consist of a single binary file.
However, TravisCI and CircleCI are commonly used for testing code, and these
services also offer running containers. So Stools combined both the concepts.
It involves spinning a Clair Scanner container during testing and building a
Singularity image, and scanning it for filesystem before the image is finalized.

In our experiments, we used a Docker image (\href{https://hub.docker.com/r/vanessa/stools-clair}{vanessa/stools-clair:v3.2.1})
for scanning and followed the steps mentioned in (\href{https://github.com/singularityhub/stools}{Stools Github})

@@

If there exist vulnerabilities in the container image, then we can
run after updating the
image. Updating the image involves updating all software packages that are
inside that image. We used a bash script (\href{https://github.com/kaurbhupinder/Vulnerability-Analysis}{Github}) 
to update all images, which checks
package manager present inside the image and then according to that it
updates the image. However, this option effects the reproducibility
of the image, which means that the image cannot be used to verify research
findings of other scientists.

@@

In this section, we present results of three experiments that are carried out to see
how the number of vulnerabilities vary inside images. First experiment involves scanning
the images. We use three different scanners
to see if all are reporting same vulnerabilities or not. Second experiment involves updating
all these images and then rescanning. The last experiment involves shrinking the size of the image
meaning that removing all unnecessary packages from the image to see the effect on the number of
vulnerabilities present inside the image.

@@

Figure~\ref{fig:venn} illustrates the number of vulnerabilities detected by scanners. The
overlapping regions of Venn diagram shows the number of common vulnerabilities detected by either two or
three scanners. In total 10691 vulnerabilities are detected by three scanners.
There are also vulnerabilities that are detected only by one scanner.

Figure~\ref{fig:graph1} gives more image specific information.
It represents the number of vulnerabilities that are present inside images.
The overall trend of the Figure shows that as the number of packages increases in the image, the number of vulnerabilities
also get increased.
The figure also infers that Alpine distribution, being the
light-weight distribution, have least number of vulnerabilities, whereas Ubuntu contains highest number of
vulnerabilities. Debian contains highest number of critical vulnerabilities among Ubuntu, Alpine, and Centos.

@@

Table~\ref{table1} compares results of scanning images with three scanners.
Venn Diagram in Figure~\ref{fig:venn} summarizes this table.

We add all regions of Venn diagram
we get total 20050 vulnerabilities in Bids and Boutiques images.
It is interesting to note that out of these vulnerabilities, 4453 vulnerabilities are only
reported by Anchore, 673 only reported by Clair and 325 only detected by Vuls.

The number and type of vulnerabilities reported by the three scanners are drastically different from each other.
The question arises why these scanners report different number and type of vulnerabilities.
How their logic differs and what exactly is making these results different than each other.

@@

\textbf{Vulnerabilities not present in Ubuntu 14.04 ESM release:} These vulnerabilities are not present in Ubuntu 14.04 ESM so they 
are not detected by Clair but they affect Ubuntu 14.04 LTS That’s why detected by Vuls. For example, CVE-2017-1375.

\textbf{False negatives by Clair:} Clair is missing vulnerabilities that it should detect. For example CVE-2016-9082 
is present in package cairo in Xenial release and it is not detected by Clair.

\textbf{False positives by Clair:} These vulnerabilities are not linked to Ubuntu 14.04 LTS which is 
present inside the image but Clair is showing because these vulnerabilities are present in Ubuntu 14.04 ESM and 
Clair is only referring to Ubuntu 14.04 ESM release. For example CVE-2019-1274.

\textbf{Database difference:} As we discussed earlier that Clair Scanner's database was old by one week.
                So some of the vulnerabilities were not updated yet. For example CVE-2019-5094, which
		was published on 2019-09-24, was not 
		updated in Clair Scanner's database that time. Due to which it is missed by Clair Scanner.

\textbf{Epoch bug:} There is a bug in the Anchore scanner due to which some vulnerabilities are 
		not detected by Anchore. This bug gets triggered when package’s version have epoch 
		(1:3.3.9-1ubuntu2.3)  in it. For example CVE-2018-1125 in procps package.

\textbf{with status as "Ignored (out of standard support)" bug:} There is another bug in Anchore due to 
		which it is not able to detect some vulnerabilities. Due to this bug Anchore does not detect 
		vulnerabilities which have a status as “ignored (out of standard support)” in Ubuntu 14.04 LTS. 
		But if this vulnerability is present in Ubuntu 14.04 ESM release it is detected by Clair. 
		For example CVE-2019-13565 in Ubuntu 14.04.

\textbf{False Negatives by Vuls:} Vuls is missing some of the vulnerabilities that it should detect. 
		For example CVE-2019-5094

\textbf{Rejected CVEs:} There are some CVE that are rejected because they are duplicate copies of another CVEs. 
	So Anchore is not reporting those rejected CVEs but Vuls is reporting those. For example CVE-2017-13753

@@

The next experiment involves updating all these images and then rescanning them to see how the number of
vulnerabilities drop inside them. We used a \textit{bash} script to update these images. This script is
present in our github repository \href{https://github.com/kaurbhupinder/Vulnerability-Analysis}
{https://github.com/kaurbhupinder/Risk-to-Clusters-Paper}. This script 
will find package manager inside the image and then update the image according the package manager it finds.
When these images are rescanned after updation, results changed drastically. However, there are still
vulnerabilities reported by these scanners but there are no fixes available for these vulnerabilities
till date so there is nothing that can be done to remove these vulnerabilties. There are only two
options, either you accept those vulnerabilities and use that image, or you discard that image.
So one thing is clear here that even if we keep our images up to date there will be still some
vulnerabilities that we have to face.
Figure~\ref{fig:graph2}shows number of vulnerabilities that are detected by Anchore after updating these images.

\begin{figure}[!htb]
        {\includegraphics[width=\columnwidth]
        {Figures/aferupdatewithpackage.png}}
        \caption{\label{fig:graph2} Scatterplot representing the number of vulnerabilities before and 
	after update of the images}
      \end{figure}
\subsection{Effect Of Size Reduction}
